Diagnostics for a generalized linear model

### 2023-02-19 text/21/glm-deviance.Rmd
Added year-end-summary.R

```{r}
fn <- "http://www.stata-press.com/data/lf2/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

[hua1]: https://francish.netlify.app/post/poisson-and-negative-binomial-regression-using-r/
[rod2]: https://data.princeton.edu/wws509/r/overdispersion
[rod3]: http://www.stata-press.com/data/lf2/couart2.dta
[sim3]: http://www.pmean.com/00files/couart2.dta
[zei1]: https://cran.r-project.org/web/packages/pscl/vignettes/countreg.pdf

```{r}
fn <- "http://www.stata-press.com/data/lf2/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

>>>>

```{r}
fn <- "http://www.pmean.com/00files/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

[hua1]: https://francish.netlify.app/post/poisson-and-negative-binomial-regression-using-r/
[rod2]: https://data.princeton.edu/wws509/r/overdispersion
[rod3]: http://www.pmean.com/00files/couart2.dta
[sim3]: http://www.pmean.com/00files/couart2.dta
[zei1]: https://cran.r-project.org/web/packages/pscl/vignettes/countreg.pdf

```{r}
fn <- "http://www.pmean.com/00files/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

### 2023-02-19 text/21/glm-diagnostics.Rmd
Added year-end-summary.R

```{r}
fn <- "http://www.stata-press.com/data/lf2/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

[hua1]: https://francish.netlify.app/post/poisson-and-negative-binomial-regression-using-r/
[rod2]: https://data.princeton.edu/wws509/r/overdispersion
[rod3]: http://www.stata-press.com/data/lf2/couart2.dta
[sim3]: http://www.pmean.com/00files/couart2.dta
[zei1]: https://cran.r-project.org/web/packages/pscl/vignettes/countreg.pdf

>>>>

```{r}
fn <- "http://www.pmean.com/00files/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

[hua1]: https://francish.netlify.app/post/poisson-and-negative-binomial-regression-using-r/
[rod2]: https://data.princeton.edu/wws509/r/overdispersion
[rod3]: http://www.pmean.com/00files/couart2.dta
[sim3]: http://www.pmean.com/00files/couart2.dta
[zei1]: https://cran.r-project.org/web/packages/pscl/vignettes/countreg.pdf
